---
title: "Statistical Functions"
author: "Christopher Agard"
date: "October 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#statMode()
##Description
This function calculates the *mode* of a vector

##Arguments
*x* takes an integer or numeric vector

### Notes:


##Next steps 
- test limits of vector types supplied to argument
- add stop functions to this function when critcal condition are not met
##code
```{r}
statMode<-function(x){
        tmp<-as.data.frame(table(x))#store tabled frequencies of values as a dataframe with colnames *x* and *Freq*
        mode<-tmp[which(tmp$Freq==max(tmp$Freq)),1]
        return(mode)
}
```
#sumstat()

##Description
This function calculates *mean*, *standard deviation (sd)*, *median*, *Inter Quartile Range*, *n*

##Arguments
*x* takes an integer or numeric vector

### Notes:
- requires the function *statMode*

##Next steps 
- test limits of vector types supplied to argument
- add stop functions to this function when critcal condition are not met
##code
```{r}
sumstat<-function(x){
        mysumresults<-list("mean"=mean(x,na.rm=T),
                           "sd"=sd(x,na.rm=T),
                           "median"=median(x,na.rm=T),
                           "iqr"=IQR(x,na.rm=T),
                           "mode"=statMode(x),
                           "n"= if(is.null(dim(x))){
                                   length(x)
                           }
                           else{
                                   nrow(x)
                                   
                           }
        )
        return(mysumresults)
}
```


