---
title: "unsorted functions"
author: "Christopher Agard"
date: "October 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#myinstallpackages()

##Description
This function checks to see if packages are installed and attempts to install those that are not already installed.  After checking and installing, *myinstall* attempts to library the packages

##Arguments
*mypackages* takes a character object or vector that names the package or packages to be installed.  
The default value is NULL.
### Notes:
- Each package must be surrounded by quotation marks(e.g.,to install and library, *read.xlsx*, myinstall("read.xlsx"))
- If multiple packages are supplied to mypackages argument, they must be supplied as a vector (e.g., to install and library *stats* and *tabular*, myinstall(c("stats","tabular"))

##Next steps 
- the argument supplied to the mypackages argument muct have each function surrounded by quotations, will attempt to allow the function to provide necessary quotations.
- this function is relatively slow, will attempt to vectorize the function in a better way to speed it up
##code
```{r}
myinstallpackages<-function(mypackages){
        neededpackages<-as.character(mypackages[which(!is.element(el=mypackages,set=installed.packages()))])
        if(length(neededpackages>0)){
                install.packages(neededpackages)
        }else{
                warning("All packages already installed")
        }
        lapply(mypackages,function(x) library(x,character.only = T))
}
```
